\documentclass{article}
\usepackage{amsmath,amssymb}
\begin{document}
\section*{Derivation 1: Klein-Gordon as the Linear Phase-Field Equation}

\textbf{Metric signature:} $(+, -, -, -)$ throughout.

The \emph{g\~{}}-Hamilton-Jacobi equation in the causal metric
$\tilde{g}_{\mu\nu} = A^2(\phi)\,\eta_{\mu\nu}$:
\[
(\partial_t S)^2 - |\nabla S|^2 = A^2(\phi)\,m^2 c^2 .
\]

Start from the \emph{linear} wave equation in the causal metric,
$(\tilde{\Box} + m^2 c^2/\hbar^2)\Psi = 0$, and insert the
WKB / eikonal ansatz
\[
\Psi = R \, e^{iS/\hbar}, \qquad R, S \in \mathbb{R} .
\]

The causal d'Alembertian for $\tilde{g}_{\mu\nu} = A^2\eta_{\mu\nu}$ is
\[
\tilde{\Box} = A^{-2}\Box_M + 2A^{-3}\,\eta^{\mu\nu}(\partial_\mu A)\,\partial_\nu ,
\]
where $\Box_M = \partial_t^2 - \nabla^2$ is the Minkowski d'Alembertian.
Dividing the wave equation by $e^{iS/\hbar}$ and collecting powers of
$\hbar$ yields three orders:

\begin{itemize}
\item \textbf{O($\hbar^{-2}$):} the Hamilton-Jacobi equation
  \[
  (\partial_t S)^2 - |\nabla S|^2 = A^2 m^2 c^2 .
  \]
\item \textbf{O($\hbar^{-1}$):} the transport equation with temporal-shear correction
  \[
  \partial_t(R^2\,\partial_t S) - \nabla\cdot(R^2\,\nabla S)
  + 2A^{-1}R^2\,\eta^{\mu\nu}(\partial_\mu A)(\partial_\nu S) = 0 ,
  \]
  i.e.~conservation of the probability current $j^\mu = R^2\,\partial^\mu S$
  modified by the temporal shear $\Sigma_\mu = \partial_\mu\ln A$.
  In the screened limit $A\to 1$, $\partial_\mu A\to 0$, this reduces to
  the standard transport equation.
\item \textbf{O($\hbar^{0}$):} the quantum-potential term with shear coupling
  \[
  A^{-2}\frac{\Box_M R}{R} + 2A^{-3}\,\eta^{\mu\nu}(\partial_\mu A)
  \frac{\partial_\nu R}{R} ,
  \]
  which reduces to $\Box_M R/R$ in the screened limit and is suppressed
  by $\hbar^2$ relative to the HJ term.
\end{itemize}

\textbf{Physical interpretation.}
The Klein-Gordon operator is recovered as the linear stationary
phase-field equation whose eikonal limit is the
$\tilde{g}$-Hamilton-Jacobi equation.  It is not derived from the HJ
equation by operator substitution; rather, the HJ equation is the
leading-order (classical) limit of the linear wave equation.

In the screened limit $A(\phi)\to 1$, $\tilde{\Box}\to\Box_M$ and the
standard Klein-Gordon equation is recovered.  In the unscreened regime
the causal d'Alembertian encodes additional temporal-shear coupling
terms proportional to $\partial_\mu A$.

\textbf{Mass parameter.}  The bare mass $m$ enters the primitive action
$S = -mc^2\int d\tilde{\tau}$.  The local oscillator frequency is
$\omega_{\rm local} = mc^2 A(\phi)/\hbar$.  The KG equation uses the
bare parameter $m$ because the conformal modulation is already
contained in $\tilde{\Box}$; the effective inertial mass measured by
local clock response reduces to $m$ when $A\to 1$.

\end{document}
